The Local Group in the Cosmic Web

### 2014-08-13 paper/main.tex
eccentricity

>>>>

We explored the main differences between the GS and RS samples which can be
producing this alignment strength feature, and we have that RS samples contraint
the tangential velocity, then pair orbits are more eccentric as we tighten pair
constraints, and for GS sample there is no tangential velocity constraint at all.
Therefore, to study any relation between orbit eccentricity and alignment, we 
computed for each halo pair in all samples, an approximate orbit 
eccentricity assuming a two body orbit with masses set as the virial 
masses and initial conditions given by current velocity vector and separation.
We found that eccentricity is not responsible for this alignement feature by
selecting a subsample of GS having the same eccentricity than 
2$\sigma$-3$\sigma$ samples, and we found no increase in the alignment of 
this subsample with GS.
